A Real-World Framework for Translator as Expert Retrieval

### 2014-07-01 docs/paper/introduction.tex
Corrections + renaming the paper folder
camera-ready version

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on a multilingual dataset. In contrast to common expert retrieval systems, we also include non-topical factors involved in the search for a translator (such as price and delivery time).% in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
 The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators are studied; and a Learning-to-Rank phase in which different features are tested under different Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application, under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}. The contributions of the report are four-fold:
\begin{enumerate}
\vspace{-0.3cm}
\item the application and adaptation of state-of-the-art IR methods to a new use-case
\item extensive evaluation in a realistic scenario, including non-topical relevance criteria as part of the evaluation
\item creation of a publicly available test collection for both of the steps involved in the retrieval framework
\vspace{-0.3cm}
\end{enumerate}

>>>>

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on a multilingual dataset. In contrast to common expert retrieval systems, we also include non-topical factors involved in the search for a translator (such as price and delivery time). % in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators are studied based on the proof-readers' assessments as gold standard; and a Learning-to-Rank phase in which different features are tested under different Learning-to-Rank methods based on a manually created ground truth, which we make available together with the gold standard and the document similarities, under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}. The contributions of the report are three-fold:
\begin{enumerate}
\vspace{-0.3cm}
\item the application and adaptation of state-of-the-art IR methods to a new use-case
\item extensive evaluation in a realistic scenario, including non-topical relevance criteria as part of the evaluation
\item creation of a publicly available test collection for both of the steps involved in the retrieval framework
\vspace{-0.3cm}
\end{enumerate}
